Figure supplements

### 2023-01-10 text/Manuscript.Rmd
Figure legend_2

![**Figure 5. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) Schematic diagram of the immunostaining procedure after calcium imaging. (B and D) The position of the cPRC in calcium imaging with GCaMP6s. Cells around the cPRC are numbered according to the position of the nuclei. (C and E) Immunostaining image using RYamide (C) or RGWamide and 5-HT antibodies (red) (E) and DAPI (cyan) in the same region as (B) or (D). IN-NOS, IN-RGWa and Ser-h1 identified from the numbered nuclear positions are shown. (F) Correlation (Pearson's r) map of neuronal activity of the cPRC, IN-NOS, IN-RGWa and Ser-h1 neurons.(E) Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in WT (dark purple) and NOS mutant (light purple) larvae. (F) Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in NIT-GC2 morphants larvae. (H) Changes over time in GCaMP6s intensities in IN-RGWa when cPRC is stimulated with UV in WT (dark blue) and NOS mutant (light blue) larvae. (I) Changes over time in GCaMP6s intensities in Ser-h1 when cPRC is stimulated with UV in WT (dark red) and NOS mutant (light red) larvae.](../figures/Fig5.png){width="100%"}

@@

![**Figure 6. Gene expressions and signalling mechanisms between cPRC, INNOS and INRGWa.** (A) Dot plot of genes (columns) expressed in three types of cells (rows) in the cPRC circuit using single cell RNA-Seq. The size of the dots is expressed in proportion to the percentage of cells expressing that gene relative to all cells. The colours represent the normal logarithm of the number of transcripts in the cells expressing the gene. (B) Schematic diagram of the signalling pathway of the cPRC circuit, focusing on the NO feedback.](../figures/Fig6.png){width="100%"}

>>>>

![**Figure 5. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** **(A)** Schematic diagram of the immunostaining procedure after calcium imaging. **(B, D)** The position of the cPRC in calcium imaging with GCaMP6s. Cells around the cPRC are numbered according to the position of the nuclei. **(C, E)** Immunostaining images using RYamide (C) or RGWamide and 5-HT antibodies (E) and DAPI (cyan) in the same region as (B) or (D). IN-NOS, IN-RGWa and Ser-h1 identified from the numbered nuclear positions are shown. **(F)** Correlation (Pearson's r) map of neuronal activity of the cPRC, IN-NOS, IN-RGWa and Ser-h1 neurons. **(G)** Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in WT (dark purple) and NOSΔ11/Δ11 mutant (light purple) larvae. **(H)** Changes over time in GCaMP6s intensities in IN-NOS when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: pink and light pink) larvae. **(I)** Changes over time in GCaMP6s intensities in IN-RGWa when cPRC is stimulated with UV in WT (dark blue) and NOSΔ23/Δ23 mutant (light blue) larvae. **(J)** Changes over time in GCaMP6s intensities in IN-RGWa when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: blue and light blue). **(K, L)** Changes over time in GCaMP6s intensities in Ser-h1 and MC when cPRC is stimulated with UV in WT (Ser-h1 and MC: dark red and brown) and NOSΔ11/Δ11 mutant (Ser-h1 and MC: light red and brown) larvae.](../figures/Fig5.png){width="100%"}

@@

![**Figure 6. Gene expressions and signalling mechanisms between cPRC, INNOS and INRGWa.** **(A)** Dot plot of genes (columns) expressed in three types of cells (rows) in the cPRC circuit using single cell RNA-Seq. The size of the dots is expressed in proportion to the percentage of cells expressing that gene relative to all cells. The colours represent the normal logarithm of the number of transcripts in the cells expressing the gene. **(B)** Schematic diagram of the signalling pathway of the cPRC circuit, focusing on the NO feedback.](../figures/Fig6.png){width="100%"}

### 2023-01-10 text/Supplements.Rmd
Figure legend_2

![**Figure 4---figure supplement 1.** Phylogenetic tree of guanylate cyclase by maximum likelihood (ML). Guanylate cyclase-coupled receptor and soluble guanylate cyclases (sGC) as outgroups. Guanylate cyclases with NIT domains are found in most animal phyla except Porifera, Ctenophora, Urochordata and Chordata.](../figures/Fig4_sup1.png){width="100%"}

>>>>

![**Figure 4---figure supplement 1.** Phylogenetic tree of guanylate cyclase by maximum likelihood (ML). Guanylate cyclase-coupled receptor and soluble guanylate cyclases (sGC) as outgroups. Guanylate cyclases with NIT domains are found in most animal phyla except Porifera, Ctenophora, Urochordata and Chordata. Dot plot of Platynereis NIT-GC genes (columns) expressed in cPRC, INNOS and INRGWa (rows) using single cell RNA-Seq. The size of the dots is expressed in proportion to the percentage of cells expressing that gene relative to all cells. The colours represent the normal logarithm of the number of transcripts in the cells expressing the gene.](../figures/Fig4_sup1.png){width="100%"}
